Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-10-14 bd_notation.tex
[review] 1. The part on conformal map reviewed, with one reference added (No worry, Stephan's light-cone paper is still at 25)
2. All the highlights removed except two places, one for the above, the other at the numerical.

3. One typo at App. A fixed.

4. Various places at the reply_to_referee highlighted, which need to be clarified.
[referee] version resubmitted to prb.

We use chemical reaction style to represent the change of boundary conditions. Taking the example of the echo diagrams in Fig.~\ref{fig:echo}, there are three boundary conditions $a,b,c$ in the folding picture, which represents the status on two ends of the chain before and after the quench. The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the conformal interface. The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ prior the quench to $b$/$c$ after the quench. Since each letter can take a general conformal interface defined by the $S$ matrix in Eq.~\eqref{eq:S1_S2}, we denote it as
\begin{equation}
S_a( \theta_a ) + S_c( \theta_c) \rightarrow S_b( \theta_b )  + S_c( \theta_c ) .
\end{equation}
\rev{In most cases of the following, we will consider taking $a = c$ to remove the bcc operator from $a$ to $c$ at infinity. And we will use the shorthand notation
\begin{equation}
S_a( \theta_a ) \rightarrow S_b( \theta_b )
\end{equation}
to remind ourselves that we are isolating the boundary condition change only on joint of the two chains. 
}

In the ``cut-and-join" protocol we considered, $a$ should be one of `DD', `DN', `ND', `NN', $b$ is taken to be $S_1( \theta )$ or $S_2( \theta )$. The physical situation of connecting two compact bosons (and our numerical simulation) corresponds to the choice of $S_1( \theta)$, and we reserve the notation $\lambda$ for this type of boundary condition. For instance, the notation for the process presented in Fig.~\ref{fig:echo} is
\begin{equation}
\label{eq:DNDN}
 {\rm DN} \rightarrow \lambda.
\end{equation}
Another interesting case is to take $a$ or $c$ to be completely transmitting interface, i.e. $S_2( \frac{\pi}{4} )$. This S-matrix corresponds to the traditional periodic boundary condition and we use symbol 'P' to denote it.

>>>>

We use chemical reaction style to represent the change of boundary conditions. Taking the example of the echo diagrams in Fig.~\ref{fig:echo}, there are three boundary conditions $a,b,c$ in the folding picture, which represents the status of the two ends of the chain before and after the quench. The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on $ab$ interface. The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ prior the quench to $b$/$c$ after the quench. Since each letter can take a general conformal interface defined by the $S$ matrix in Eq.~\eqref{eq:S1_S2}, we denote it as
\begin{equation}
\label{eq:Full_notation_rand()}
S_a( \theta_a ) + S_c( \theta_c) \rightarrow S_b( \theta_b )  + S_c( \theta_c ) .
\end{equation}
In most cases of the following, we will consider taking $a = c$ to remove the bcc operator from $a$ to $c$ at infinity. And we will use the shorthand notation
\begin{equation}
S_a( \theta_a ) \rightarrow S_b( \theta_b )
\end{equation}
to remind ourselves that we are isolating the boundary condition change only on the joint of the two chains.

In the ``cut-and-join" protocol we considered, $a$ should be one of `DD', `DN', `ND', `NN', $b$ is taken to be $S_1( \theta )$ or $S_2( \theta )$. The physical situation of connecting two compact bosons (and our numerical simulation) corresponds to the choice of $S_1( \theta)$, and we reserve the notation $\lambda$ for this type of boundary condition. For instance, the notation for the process presented in Fig.~\ref{fig:echo} is
\begin{equation}
\label{eq:DNDN}
 {\rm DN} \rightarrow \lambda.
\end{equation}
Another interesting case is to take $a$ or $c$ to be a completely transmitting interface, i.e. $S_2( \frac{\pi}{4} )$. This $S$-matrix corresponds to the traditional periodic boundary condition and we use symbol 'P' to denote it.

### 2017-10-14 compact_boson.tex
[referee] version resubmitted to prb.

We recall that the gluing condition is written as
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}.
\end{aligned}
\end{equation}
Upon folding $\phi^2$ to the negative axis, its $\partial_x$ derivative becomes $-\partial_x$, so 
\begin{equation}
\begin{bmatrix}
\partial_{+} \phi^1 \\
\partial_{+} \phi^2 \\
\end{bmatrix}
 = S
\begin{bmatrix}
\partial_{-} \phi^1 \\
\partial_{-} \phi^2 \\
\end{bmatrix}.
\end{equation}
In terms of the holomorphic coordinates defined in Eq.~\eqref{eq:zzbar}, 
\begin{equation}
\partial_{+} = \frac{4\pi i }{T} \bar{z} \partial_{\bar{z}} ,\qquad \partial_{-} = -\frac{4\pi i }{T} z\partial_{z},
\end{equation}
the $S$ matrix establish a relation between the modes
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
\bar{a}_n^1\bar{z}^{-n}\\
\bar{a}_n^2\bar{z}^{-n}
\end{pmatrix}
= -S(\theta)
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
a_n^1{z}^{-n}\\
a_n^2{z}^{-n}
\end{pmatrix}.
\end{aligned}
\end{equation}
At the boundary $x = 0$, $\bar{z}=z^{-1}$, therefore we have
\begin{equation}
\begin{aligned}
a^i_n + (S^{-1}_{ij})\bar{a}^j_{-n}=0.
\end{aligned}
\end{equation}
The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}.

We specialize to $S = S_1$ to solve the $ n = 0$ constraint. We introduce the compactification lattice and its dual\cite{affleck_quantum_2001,oshikawa_boundary_2010}
\begin{equation}
\label{eq:lattice}
\vec{M} = (m_1 2 \pi R_1, m_2 2\pi  R_2)^\top, \quad  \vec{M}^* = (\frac{n_1}{R_1}, \frac{n_2}{R_2})^\top,
\end{equation}
to rewrite the zero mode part as 
\begin{equation}
  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \,\, \implies \,\, ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* ),
\end{equation}
which is basically the multi-component boson winding constraints given in \onlinecite{affleck_quantum_2001,oshikawa_boundary_2010}. The solution gives the interface parameter $\lambda$
\begin{equation}
\begin{aligned}
\label{eq:S_1_constraint}
\lambda = \tan\theta=\frac{n_2R_1}{n_1R_2}=-\frac{m_1R_1}{m_2R_2},
\end{aligned}
\end{equation}
and the conformal boundary state
\begin{equation}\begin{aligned}
\label{eq:S1bd-state}
g_{S_1}\sum_{S_1}e^{in_1\phi_0-im_1\bar{\phi}_0}|n_1,m_1\rangle|n_2,m_2\rangle,
\end{aligned}\end{equation}
where $\sum_{S_1}$ is the summation consistent with the constraint in Eq.~\eqref{eq:S_1_constraint}. The g-factor can only be determined by the Cardy condition\cite{cardy_boundary_2004}. Since it is not important for what follows, we shall not include the calculation here.

@@

\subsection{Winding Mode Contribution to the Partition Function}
\label{app_sub:winding_contribution}
We now calculate the winding mode part of the partition function as shown in Fig.~\ref{fig:fig_lambda_1_lambda_2}
\begin{equation}\begin{aligned}
Z=\langle S_j( \theta_2 )|e^{-\pi H}|S_i(\theta_1 )\rangle,\qquad H=\frac{2\pi}{\beta}(L_0+\bar{L}_0).
\end{aligned}\end{equation}
With boundary state, we can simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$).

>>>>

We recall that the gluing condition is written as
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}.
\end{aligned}
\end{equation}
Upon folding $\phi^2$ to the negative axis, its $\partial_x$ derivative becomes $-\partial_x$, so 
\begin{equation}
\begin{bmatrix}
\partial_{+} \phi^1 \\
\partial_{+} \phi^2 \\
\end{bmatrix}
 = S
\begin{bmatrix}
\partial_{-} \phi^1 \\
\partial_{-} \phi^2 \\
\end{bmatrix}.
\end{equation}
In terms of the holomorphic coordinates defined in Eq.~\eqref{eq:zzbar}, 
\begin{equation}
\partial_{+} = \frac{4\pi i }{T} \bar{z} \partial_{\bar{z}} ,\qquad \partial_{-} = -\frac{4\pi i }{T} z\partial_{z},
\end{equation}
the $S$ matrix establish a relation between the modes
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
\bar{a}_n^1\bar{z}^{-n}\\
\bar{a}_n^2\bar{z}^{-n}
\end{pmatrix}
= -S(\theta)
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
a_n^1{z}^{-n}\\
a_n^2{z}^{-n}
\end{pmatrix}.
\end{aligned}
\end{equation}
At the boundary $x = 0$, $\bar{z}=z^{-1}$, we have
\begin{equation}
\begin{aligned}
a^i_n + (S^{-1}_{ij})\bar{a}^j_{-n}=0.
\end{aligned}
\end{equation}
The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}.

We specialize to $S = S_1$ to solve the $ n = 0$ constraint. We introduce the compactification lattice and its dual\cite{affleck_quantum_2001,oshikawa_boundary_2010}
\begin{equation}
\label{eq:lattice}
\vec{M} = (m_1 2 \pi R_1, m_2 2\pi  R_2)^\top, \quad  \vec{M}^* = (\frac{n_1}{R_1}, \frac{n_2}{R_2})^\top,
\end{equation}
to rewrite the zero mode part as 
\begin{equation}
  a_0^i + S^{-1} _{ij} \bar{a}_{0}^j = 0 \,\, \implies \,\, ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* ),
\end{equation}
which is basically the multi-component boson winding constraints given in \onlinecite{affleck_quantum_2001,oshikawa_boundary_2010}. The solution gives the interface parameter $\lambda$
\begin{equation}
\begin{aligned}
\label{eq:S_1_constraint}
\lambda = \tan\theta=\frac{n_2R_1}{n_1R_2}=-\frac{m_1R_1}{m_2R_2},
\end{aligned}
\end{equation}
and the conformal boundary state
\begin{equation}\begin{aligned}
\label{eq:S1bd-state}
g_{S_1}\sum_{S_1}e^{in_1\phi_0-im_1\bar{\phi}_0}|n_1,m_1\rangle|n_2,m_2\rangle,
\end{aligned}\end{equation}
where $\sum_{S_1}$ is the summation consistent with the constraint in Eq.~\eqref{eq:S_1_constraint}. The g-factor can only be determined by the Cardy condition\cite{cardy_boundary_2004}. Since it is not important for what follows, we shall not include the calculation here.

@@

\subsection{Winding Mode Contribution to the Partition Function}
\label{app_sub:winding_contribution}
We now calculate the winding mode part of the partition function as shown in Fig.~\ref{fig:fig_lambda_1_lambda_2}
\begin{equation}\begin{aligned}
Z=\langle S_j( \theta_2 )|e^{-\pi H}|S_i(\theta_1 )\rangle,\qquad H=\frac{2\pi}{\beta}(L_0+\bar{L}_0).
\end{aligned}\end{equation}
For boundary states, we can simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$).

### 2017-10-14 conclusion.tex
[referee] version resubmitted to prb.

We began by classifying the boundary states by two types of $S$ matrices $S_1(\theta)$ and $S_2(\theta)$, where the parameter $\theta$ -- the scattering angle -- is determined by the transmission coefficient of the interface. The conventional `DD', `NN' boundary conditions belong to special choice of $\theta$ in $S_1$ and  `DN' and P belongs to $S_2$. Generic value of $\theta$ then interpolates between those conventional boundary conditions. A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions in a concrete lattice setting.

The dynamical behavior of the Loschmidt echo reflects the change of the conformal interface during the process described in {\color{red}Eq.~\eqref{eq:S_i_S_j}}.
%, which we denote as
%\begin{equation}
%S_i( \theta_1 ) \rightarrow S_j( \theta_2 )  \quad i, j = 1, 2. 
%\end{equation}
Its power law decay exponent is related to the scaling dimension of the bcc operator that mediates these interfaces. Analytic computation shows that the exponent is always $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices ($i \ne j$), regardless of the choice of $\theta$. On the other hand, the exponent depends on the difference of angles $\theta_1 - \theta_2$ as a quadratic relation when the change is made between the same types of $S$ matrices ($i = j$).

These two features were tested in three typical processes in the numerical calculation of the harmonic chains. After using suitable regulators for the zero-mode problem, the numerical results agreed with the analytic calculation within error. Although tangential to the non-equilibrium dynamics, the fidelity calculation was used as a diagnostic tool and shows better agreement of the exponent, providing more confidence about our analytic results.

We proposed that the Loschmidt echo exponent in principle should be detectable in an X-ray edge singulrity type experiment on quantum wires systems.

>>>>

We began by classifying the boundary states by two types of $S$ matrices $S_1(\theta)$ and $S_2(\theta)$, where the parameter $\theta$ -- the scattering angle -- is determined by the transmission coefficient of the interface. The conventional `DD', `NN' boundary conditions are among the special choices of $\theta$ in $S_1$, and `DN' and P are among the special choices of $S_2$. Generic value of $\theta$ then interpolates between those conventional boundary conditions. A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions in a concrete lattice setting.

The dynamical behavior of the Loschmidt echo reflects the change of the conformal interfaces during the process described in Eq.~\eqref{eq:S_i_S_j}.
%, which we denote as
%\begin{equation}
%S_i( \theta_1 ) \rightarrow S_j( \theta_2 )  \quad i, j = 1, 2. 
%\end{equation}
Its power law decay exponent is related to the scaling dimension of the bcc operator that mediates the interfaces. Analytic computation shows that the exponent is always $\frac{1}{4}$ when the change of boundary conditions is made between different types of $S$ matrices ($i \ne j$), regardless of the choice of $\theta$. On the other hand, the exponent depends on the difference of angles $\theta_1 - \theta_2$ as a quadratic relation when the change is made between the same type of $S$ matrices ($i = j$).

These two features are tested in three typical processes in the numerical calculation of the harmonic chains. After using suitable regulators for the zero-mode problem, the numerical results agreed with the analytic calculation within error. Although tangential to the non-equilibrium dynamics, the fidelity calculation was used as a diagnostic tool and shows better agreement of the exponent, providing more confidence about our analytic results.

We proposed that the Loschmidt echo exponent in principle should be detectable in an X-ray edge singulrity type experiment on the quantum wire systems.

### 2017-10-14 def_fidel_echo.tex
[referee] version resubmitted to prb.

Fidelity is the square of the overlap of the groundstates of two Hamiltonians, 
\begin{equation}
{\rm fidelity} \equiv |\langle \psi_1 |\psi_2  \rangle |^2 .
\end{equation}
For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chains (of equal length $L$, hence ``bipartite") and $|\psi_2\rangle$ is that of the connected chains with conformal interface. Both of them can be produced by an imaginary time evolution. Taking the horizontal axis as imaginary time direction, the fidelity can be diagrammatically represented in Fig.~\ref{fig:fidel}, where the slits represent the disconnected boundary conditions, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$. The logarithmic fidelity is then (twice) the free energy of this diagram
\begin{equation}
\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln |Z|.
\end{equation}

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{fig_fidelity-DN-lambda-folding.pdf}
\caption{Fidelity of connecting two CFTs. The horizontal axis is the imaginary time. Evolution along the two semi-infinite stripes produces the groundstates of the disconnected and connected chain Hamiltonians. The right diagram is the result of folding the lower part of the diagram up, so that all the boundaries are now boundary states. The solid dot represents boundary condition changing (bcc) operator. Here D(Dirichlet), N(Neumman), $\lambda$(permeable interface parameterized by $\lambda$ are possible choices of boundary conditions.)}
\label{fig:fidel}
\end{figure}

The Loschmidt echo is also the (square of the) overlap of two wavefunctions. One of the them is the groundstate of the disconnected chains and the other is the groundstate evolved by the Hamiltonian of the connected chains
\begin{equation}
\mathcal{L}( t )  \equiv |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2 .
\end{equation}
The imaginary time version $\mathcal{L}( \tau  ) = |\langle \psi_{\rm gnd}  | e^{-H \tau } | \psi_{\rm gnd} \rangle|^2$ has a path integral definition similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~\ref{fig:echo}. Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt echo is also the associated free energy. After obtaining the free energy in imaginary time, we can analytically continue back to real time and get the $t$ dependence. For simplicity and comparison with the fidelity result, we will take the length of both of the chains to be $L$ and set $L \gg t$, leaving $t$ the only length scaling in the echo calculation (Fig.~\ref{fig:H-tau_fold}). The dependence on nonzero $\frac{t}{L}$ and the asymmetry of the lengths of the chains will not be discussed here (see their treatment in Ref.~\onlinecite{stephan_local_2011} for special values of $\lambda$).

\begin{figure}[h]
\centering
\includegraphics[width=1\columnwidth]{fig_echo-DN-lambda-folding.pdf}
\caption{Loschmidt echo of connecting two CFTs. Evolution along the two infinitely extended sides produces the groundstate of the disconnected chain Hamiltonians. They sandwich the evolution of the connected chains. In the folding picture at the right, a,b,c represent the most general boundary conditions of the chains (for example, $a$ and $c$ are DN according to the left figure). See the discussion in main text.}
\label{fig:echo}
\end{figure}

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slit can be regarded as a corner singularity. According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularity will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or integration of the Ward identity. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\begin{aligned}
  \mathcal{F}({\rm fidelity}) &=  \frac{c}{8} \ln L, \\
 \mathcal{F}( {\rm echo} )  &= \frac{c}{4} \ln |\tau| \rightarrow \frac{c}{4} \ln |it + \epsilon|   \sim \frac{c}{4}\ln t ,
\end{aligned}
\end{equation}
where we have performed analytic continuation $\tau \rightarrow it + \epsilon$ with $\epsilon \rightarrow 0$ for echo.

With the presence of the conformal interface, the tip of the slit is no longer a corner singularity\cite{cardy_finite-size_1988} . Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram. From the boundary CFT point of view, the change of boundary condition can be regarded as inserting a primary field which is a bcc operator. The diagrams for fidelity and echo then become the one point or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.

>>>>

Fidelity is the square of the overlap of the groundstates of the two Hamiltonians, 
\begin{equation}
{\rm fidelity} \equiv |\langle \psi_1 |\psi_2  \rangle |^2 .
\end{equation}
For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chains (of equal length $L$, hence ``bipartite") and $|\psi_2\rangle$ is that of the connected chains with conformal interface. Both of them can be produced by an imaginary time evolution. Taking the horizontal axis as imaginary time direction, the fidelity can be diagrammatically represented in Fig.~\ref{fig:fidel}, where the slits represent the disconnected boundary conditions, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$. The logarithmic fidelity is then (twice) the free energy of this diagram
\begin{equation}
\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln |Z|.
\end{equation}

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{fig_fidelity-DN-lambda-folding.pdf}
\caption{Fidelity of connecting two CFTs. The horizontal axis is the imaginary time. Evolution along the two semi-infinite stripes produces the groundstates of the disconnected and connected chain Hamiltonians. The right diagram is the result of folding the lower part of the diagram up, so that all the boundaries are now boundary states. The solid dot represents boundary condition changing (bcc) operator. Here D(Dirichlet), N(Neumman), $\lambda$(permeable interface parameterized by $\lambda$) are possible choices of boundary conditions.}
\label{fig:fidel}
\end{figure}

The Loschmidt echo is also the (square of the) overlap of two wavefunctions. One of them is the groundstate of the disconnected chains and the other is the groundstate evolved by the Hamiltonian of the connected chains
\begin{equation}
\mathcal{L}( t )  \equiv |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2 .
\end{equation}
The imaginary time version $\mathcal{L}( \tau  ) = |\langle \psi_{\rm gnd}  | e^{-H \tau } | \psi_{\rm gnd} \rangle|^2$ has a path integral definition similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~\ref{fig:echo}. Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt echo is also the associated free energy. After obtaining the free energy in imaginary time, we can analytically continue back to real time to get the $t$ dependence. For simplicity and comparison with the fidelity result, we will take the length of both of the chains to be $L$ and set $L \gg t$, leaving $t$ the only length scale in the echo calculation (Fig.~\ref{fig:H-tau_fold}). The dependence on nonzero $\frac{t}{L}$ and the asymmetry of the lengths of the chains will not be discussed here (see the treatment in Ref.~\onlinecite{stephan_local_2011} for special values of $\lambda$).

\begin{figure}[h]
\centering
\includegraphics[width=1\columnwidth]{fig_echo-DN-lambda-folding.pdf}
\caption{Loschmidt echo of connecting two CFTs. Evolution along the two infinitely extended sides produces the groundstate of the disconnected chain Hamiltonians. They sandwich the evolution of the connected chains. In the folding picture at the right, $a,b,c$ represent the most general boundary conditions of the chains (for example, $a$ and $c$ are DN according to the left figure).}
\label{fig:echo}
\end{figure}

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slit can be regarded as a corner singularity. According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularity will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in the fidelity and $\ln \tau$ in the Loschmidt echo. One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or the integration version of the Ward identity. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\begin{aligned}
  \mathcal{F}({\rm fidelity}) &=  \frac{c}{8} \ln L, \\
 \mathcal{F}( {\rm echo} )  &= \frac{c}{4} \ln |\tau| \rightarrow \frac{c}{4} \ln |it + \epsilon|   \sim \frac{c}{4}\ln t ,
\end{aligned}
\end{equation}
where we have performed analytic continuation $\tau \rightarrow it + \epsilon$ with $\epsilon \rightarrow 0$ for echo.

With the presence of the conformal interface, the tip of the slit is no longer a corner singularity\cite{cardy_finite-size_1988} . Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both the fidelity and echo diagrams. From the boundary CFT point of view, the change of boundary conditions can be regarded as inserting a bcc operator. The diagrams for the fidelity and echo then become the one point or two point functions of the bcc operators respectively, and the free energy's leading logarithmic term extracts their scaling dimensions.
